\section{Biblography}

\bibliographystyle{amsplain}

\begin{thebibliography}{9}

\bibitem{sanchez09}
  González Sánchez, J. L., Montero, F., Padilla Zea, N., Gutiérrez, F. L.,
  \emph{Playability as Extension of Quality in Use in Video Games}.
  Proceedings of 2nd International Workshop on the Interplay between
  Usability Evaluation and Software Development (I-USED), paper number 6.
  Uppsala, Sweden,
  24th August (2009)


\bibitem{hunicke01-04}
  Robin Hunicke, Marc LeBlanc, Robert Zubek,
  \emph{MDA: A Formal Approach to Game Design and Game Research}.
  Developed and taught as part of the Game Design and Tuning
  Workshop at the Game Developers Conference,
  San Jose,
  2001-2004

\bibitem{hagen10}
  Hagen, U.,
  \emph{Designing for Player Experience - How Professional Game Developers
    Communicate Design Visions.},
  Nordic DiGRA.
  2010

\bibitem{nacke09}
  Nacke, L.E., Drachen, A., Kuikkaniemi, K., Niesenhaus, J.,
  Korhonen, H.J., van den Hoogen, W.M., Poels, K., IJsselsteijn, W.A., \&
  de Kort, Y.A.W.
  \emph{Playability and Player Experience Research. DiGRA 2009, Breaking New Ground:
    Innovation in Games, Play, Practice and Theory},
  Brunel University, West London, United Kingdom,
  Tuesday 1st September - Friday 4th September 2009.

\bibitem{portnow}
  Game designer James Portnow, animator Daniel Floyd, and artists
  Allison Theus and Elisa Scaldaferri,
  \emph{Extra Credits Season 3, Ep. 21}
  Playtesting. Extra Credits is a ongoing webseries. The series of
  videos discuss issues pertinent to video games and game studies,
  particularly discussing issues concerning the development of video
  games. The show is currently published on PATV, a distribution channel
  hosted by the creators of Penny Arcade.
%FIXME link?

\bibitem{desurvire08}
  Desurvire, H., Chen, B.
  \emph{48 Differences Between Good and Bad Video Games: Game Playability Principles
    (PLAY) For Designing Highly Ranked Video Games},
  2008

\end{thebibliography}
