\section{Game description}

This section will cover the game rules, the (un)implemented features,
and the technical challenges of making the game.

\subsection{Game rules}
To complete a level, the player must obtain the goal (``gold coin''),
return to start and enter the time machine.  Each turn, the player can
do one of the following moves:

\begin{itemize}
\item Stand still (i.e. ``do nothing'')
\item Attempt to move to a neighbouring square (i.e. up, down, left or right)
\item Enter time machine (only allowed on top of the time-machine)
\end{itemize}

The player can push a crate by moving ``into'' it provided that the
destination for the crate is available.  It is not possible to
``pull'' crates and the player can push at most one crate.  These
are basically the same rules used in Sokoban for moving crates.

\paragraph{Time jumping}
The player has the ability to go back in time to the first turn.  As
the player goes back in time, the world will reset it self to its
initial state, but with one crucial difference.

There is now an extra player in the level; namely the ``current self''
that performed the time jump and the ``past self/selves''.  The latter
will carry out their actions (as the player did in that time jump) and
eventually enter the time machine.

All ``selves'' are identically in terms of play rules (e.g. any of
them can pick up the goal).  The only difference is that the player
actively controls the ``current self''.

Time jumping allows the player to do things that would not otherwise
be possible, though at the risk of introducing temporal paradoxes.

\subsubsection{Losing}

There are three different ways of losing.

\paragraph{Getting stuck}
If the player gets stuck and is unable to return to start, it is not
possible to win.  If the player gets stuck in a closed gate or a
crate, the game will automatically mark the game as lost.

If the player simply manages to ``lock himself/herself into a corner''
with no path back to start, the game will still continue (despite being
unsolvable) until the player restarts/gives up.

\paragraph{Temporal paradox}
As the name suggests, a temporal paradox (``time paradox'') is a bad
thing.  What happens if your current self prevent your past self from
becoming the current self?  In this game, you simply lose.

\paragraph{Non-Determinism}
All valid actions are carried out ``simultaneously''.  If one (or
more) valid action(s) causes another valid action to fail, the result
is non-deterministic.

As an example, consider if two clones attempt to push the same
crate.  This gives 3 cases, of which one is non-deterministic.

\begin{itemize}
\item Both clones pushes it in the same direction (i.e. they perform
  the same action and start on the same field), the actions are
  deterministic and will be carried out.
\item Both clones pushes it in opposite directions.  In this case,
  both actions are ``invalid'' because each clone can conclude (before
  pushing) that the move will not work.  This is deterministic and
  result in none of the clones moving.
\item The clones pushes it in ortogonal directions.  This causes
  non-determinism as each clone believe the action is valid, but
  both actions cannot be carried out.
\end{itemize}

This rule is (also) a generalization of getting stuck in a gate or
crate.

\subsubsection{Scoring}
The player is scored on the number of moves performed and the number
of time jumps used.  For comparsion, the lowest score is considered
best (i.e. most efficient).  The scoring rules are:

\begin{itemize}
\item 1 point per move or skipped turn by the ``current self''.
  Entering the time machine counts as a move.
\item 1 point per skipped turn while the ``current self'' is outside
  the time machine.  0 points if the ``current self'' is inside the
  time machine.
\item 1 point for every time jump performed.
\end{itemize}

\subsection{Desired features}

\subsection{Technical challenges}

